\chapter*{Dédicaces}
\addcontentsline{toc}{chapter}{Dedication}

\begin{center}
\textit{I dedicate this project to those who are dearest to me.}
\end{center}

\bigskip

\begin{center}\textbf{To my parents, Rachida and Khaireddine,}\end{center}
Who have sacrificed so much for me, often in silence and without expectation,
and who have faced life's hardships with quiet strength and grace. Your love,
guidance, and constant support have shaped who I am today, and you will always
remain the foundation of everything I have achieved and everything I hope to become.

\bigskip

\begin{center}\textbf{To my Sister Amani and my Brother Oussema,}\end{center}
For their constant support, love, and presence throughout every stage of my life.
Your encouragement, understanding, and kindness have always been a source of comfort
and strength, especially in the most difficult moments of this journey.

\bigskip

\begin{center}\textbf{To my little niece Misso,}\end{center}
Whose innocent presence and pure joy have brought light to even the most demanding
days of deadlines and long nights. Your smiles, in their simplicity, have been a
gentle reminder of hope, warmth, and the beauty found in life's smallest moments.

\bigskip

\begin{center}\textbf{To Maker Labs,}\end{center}
For the wonderful times, the laughter, the trips, and all the unforgettable memories
shared along this journey. You have been more than just a place of learning; a space
of growth, discovery, and connection. And especially to one dearest to me, who taught
me, in their own quiet way, patience, understanding, and the depth of support that
leaves a lasting mark on the heart.

\vfill
\begin{flushright}
\textit{Yessmine HASSAD}
\end{flushright}