\chapter*{Dedication}
\addcontentsline{toc}{chapter}{Dedication}

\begin{center}
\textit{I dedicate this work:}
\end{center}
\begin{center}\textbf{To my parents, Omar and Latifa, and my sister Mariem,}\end{center}
Your love, your patience, and your unwavering faith in me have been the foundation
of my perseverance. This project is above all the fruit of your silent sacrifices
and your steadfast support.
\bigskip
\begin{center}\textbf{To my beloved club: Club Africain,}\end{center}
More than a passion, a true school of life. Through its colours, its history, and
its values, I have learned resilience, loyalty, the fighting spirit, and the love
of challenge. Thank you for being a constant source of inspiration and pride.
\bigskip
\begin{center}\textbf{To the people of Club Africain, in the stadium stands,}\end{center}
Your chants, your fervour, and your unshakeable loyalty have always inspired me.
In every cry, every flag raised high, I have drawn strength, passion, and a deep
sense of belonging. Thank you for that unique energy that transcends pitches and
borders.
\bigskip
\begin{center}\textbf{To my friend Yessmine,}\end{center}
Thank you for your support, your encouragement, and the wonderful moments we shared
throughout this internship. Working alongside you as my PFE partner has been a true
pleasure, and I am grateful for the trust, the teamwork, and the friendship we have
built together.
\bigskip
\begin{center}\textbf{To my friends,}\end{center}
Thank you for your support, your encouragement, and the moments of joy shared
throughout my university journey. Your friendship has been a driving force and a
constant source of good spirits.
\bigskip
\begin{center}\textbf{To my club: Club Maker Labs,}\end{center}
More than a club: a space of passion, sharing, and self-surpassing.

\vfill
\begin{flushright}
\textit{Ifraj OUNI}
\end{flushright}