\chapter*{General Introduction}
\markboth{General Introduction}{}
\addcontentsline{toc}{chapter}{General Introduction}

In an era marked by rapid technological advancement and exponential data
growth, organizations face increasing challenges in transforming information
into actionable knowledge. AI-powered systems are reshaping how professionals
interact with complex data, enabling faster analysis and more informed
decision-making.

Within this evolving landscape, Jade Advisory, a consulting firm
specializing in Public-Private Partnerships (PPP), manages a large and
diverse portfolio of strategic documents essential for project execution
and compliance. However, their growing volume, multilingual nature, and
heterogeneous formats make information retrieval slow, fragmented, and
difficult to standardize, limiting knowledge reuse and reducing operational
efficiency.

To address this challenge, this project proposes \textbf{Ask-Jade}, a dedicated 
document management and question-answering system based on a 
Retrieval-Augmented Generation (RAG) architecture. By focusing on advanced 
document parsing, structured data ingestion, and semantic indexing, the system 
transforms Jade Advisory's document library into a central, searchable knowledge 
base, enabling fast, precise, and context-grounded access to organizational 
assets.

This report has been prepared as part of the end-of-study internship and
in fulfillment of the requirements for the degree in Software Engineering.
It is organized into five chapters, reflecting the methodological approach
followed during its development:

\begin{itemize}

  \item \textbf{Chapter 1} titled \textbf{``Project Context''} introduces the host
        company, examines the limitations of existing knowledge management
        tools, presents the proposed Ask-Jade solution, and describes the
        document dataset used to build the knowledge base.

  \item \textbf{Chapter 2} titled \textbf{``Needs Analysis and Conceptual Study''}
        defines the functional and non-functional requirements of Ask-Jade,
        identifies the system actors, and presents the use case, activity,
        and sequence diagrams.

  \item \textbf{Chapter 3} titled \textbf{``Generative AI : State of the Art''}
        presents the key technologies underlying the system, including
        Large Language Models, the RAG architecture, the BGE-M3 embedding
        model, and the evaluation approaches adopted in the project,
        namely expert evaluation and the LLM-as-a-Judge framework..

  \item \textbf{Chapter 4} titled \textbf{``Ask-Jade Pipeline''} details the two
        core pipelines of the system: the ingestion pipeline, which indexes
        documents into a vector store, and the retrieval pipeline, which
        processes user queries through multi-query expansion, RRF fusion,
        reranking, and grounded answer generation.

  \item \textbf{Chapter 5} titled\textbf{ ``Implementation and Evaluation''}
        presents the technical environment, the system interfaces for each
        use case, and the evaluation results obtained through automated
        LLM-as-a-Judge metrics and expert assessment.

\end{itemize}

Finally, a general conclusion summarizes the work accomplished, presents
the key results obtained, and outlines potential future improvements
to the Ask-Jade system.